Improving the portuguese hyphenation rules

### 2023-07-13 article/article.tex
fix #13
fix #14

Unfortunately, some specific hyphenation rules are not possible to be
implemented using the \TeX{} hyphenation algorithm. In German, for example,
when words are hyphenated, some letters might change or a letter might be
inserted.  Compound words have no hyphens, leading to long sequences of letters
with no visible separation and even repetitions of a same letter, such as in
\emph{Wasserrinne} and \emph{Schifffahrt}. Furthermore, the German spelling
reform made some changes, making it necessary to create a different set of
rules for German hyphenation.  For example, the word \emph{Schiffahrt} should
be hyphenated as \emph{Schiff-fahrt}, preserving the \emph{f}s from each word
that makes this compound. The hyphenation should insert a \emph{f} that is not
part of the written form. That was not a problem for the old written form of
the word: \emph{Schifffahrt}. Also, the old hyphenating rules of German grammar
stated the hyphenation \emph{Bäk-ker} for the word \emph{Bäcker},
\emph{Zuk-ker} for the word \emph{Zucker} and \emph{pak-ken} for the word
\emph{packen}. Now those words are hyphenated as \emph{Bä-cker}, \emph{Zu-cker}
and \emph{pa-cken}, respectively. Some words have also changed their
hyphenation point after the spelling reform. For example, \emph{Fen-ster}
became \emph{Fens-ter}and \emph{mei-stens} became \emph{meis-tens}. Some
problems in compound word hyphenation in \TeX{} are discussed in
\cite{sojka1995a}.

@@

\section{Patterns for \TeX{} hyphenation}\label{sec-patt4TeX} 
The patterns used in \TeX{} hyphenation are of the form: \texttt{4z1z2}. Each
pattern is made of a sequence of letters and numbers. Odd numbers indicate a
good hyphenation point, whereas even numbers indicate a bad place to break.
The given example states that the sequence has a good breaking point between
the first and the second \emph{z} and an hyphenation should be inhibited before
the first \emph{z} and after the second \emph{z}. For example, the hyphenation
of the word \emph{piz-za}, \emph{fiz-zle} and \emph{mezzanine} use this rule,
where we see the hyphen placed between the two \emph{z}'s and no hyphen before,
nor after the \emph{z}'s. The pattern may also use period symbol (\emph{.}) to
indicate word boundaries. The pattern \texttt{.s2h2} applies to beginning of
words, implying that the \emph{s} and the \emph{h} should stick together in
beginning of a word and an hyphenation should also be inhibited after the
\emph{h}. For example, this pattern is used in \emph{Sher-lock}.

>>>>

Unfortunately, some specific hyphenation rules are not possible to be
implemented using the \TeX{} hyphenation algorithm. In German, for example,
when words are hyphenated, some letters might change or a letter might be
inserted.  Compound words have no hyphens, leading to long sequences of letters
with no visible separation and even repetitions of a same letter, such as in
\emph{Wasserrinne} and \emph{Schifffahrt}. Furthermore, the German spelling
reform made some changes, making it necessary to create a different set of
rules for German hyphenation.  For example, the word \emph{Schiffahrt} should
be hyphenated as \emph{Schiff-fahrt}, preserving the \emph{f}s from each word
that makes this compound. The hyphenation should insert a \emph{f} that is not
part of the written form. That was not a problem for the old written form of
the word: \emph{Schifffahrt}. Also, the old hyphenating rules of German grammar
stated the hyphenation \emph{Bäk-ker} for the word \emph{Bäcker},
\emph{Zuk-ker} for the word \emph{Zucker} and \emph{pak-ken} for the word
\emph{packen}. Now those words are hyphenated as \emph{Bä-cker}, \emph{Zu-cker}
and \emph{pa-cken}, respectively. Some words have also changed their
hyphenation point after the spelling reform. For example, \emph{Fen-ster}
became \emph{Fens-ter} and \emph{mei-stens} became \emph{meis-tens}. Some
problems in compound word hyphenation in \TeX{} are discussed in
\cite{sojka1995a}.

@@

\section{Patterns for \TeX{} hyphenation}\label{sec-patt4TeX} 
The patterns used in \TeX{} hyphenation are of the form: \texttt{4z1z2}. Each
pattern is made of a sequence of letters and numbers. Odd numbers indicate a
good hyphenation point, whereas even numbers indicate a bad place to break.
The given example states that the sequence has a good breaking point between
the first and the second \emph{z} and an hyphenation should be inhibited before
the first \emph{z} and after the second \emph{z}. For example, the hyphenation
of the word \emph{piz-za}, \emph{fiz-zle} and \emph{mez-zanine} use this rule,
where we see the hyphen placed between the two \emph{z}'s and no hyphen before,
nor after the \emph{z}'s. The pattern may also use period symbol (\emph{.}) to
indicate word boundaries. The pattern \texttt{.s2h2} applies to beginning of
words, implying that the \emph{s} and the \emph{h} should stick together in
beginning of a word and an hyphenation should also be inhibited after the
\emph{h}. For example, this pattern is used in \emph{Sher-lock}.
